Twisted eleven-dimensional supergravity

### 2021-10-26 draft.tex
abs

\title{Twisted eleven-dimensional supergravity}
\author{Surya Raghavendran}
\address{Perimeter Institute for Theoretical Physics \\ 31 Caroline Street North \\ 
Waterloo, Ontario N2L 2Y5\\ Canada}
\email{sraghavendran@perimeterinstitute.ca}
\author{Ingmar Saberi}
\address{Ludwig-Maximilians-Universit\"at M\"unchen \\ Fakult\"at f\"ur Physik \\ Theresienstra\ss{}e 37 \\ 80333 M\"unchen \\ Deutschland}
\email{i.saberi@physik.uni-muenchen.de}
\author{Brian R. Williams}
\address{School of Mathematics \\ University of Edinburgh \\ Edinburgh EH9 3FD \\ Scotland}
\email{brian.williams@ed.ac.uk}
\begin{abstract}
We construct a fully interacting partially holomorphic, partially topological, theory in eleven dimensions that is defined on products of Calabi--Yau fivefolds with real one-manifolds. 
%The theory is a deformation of a BF theory based on divergence-free holomorphic vector fields on the fivefold. 
The theory describes, in part, a particular deformation of the moduli space of complex structures on the fivefold.
Its field content matches the holomorphic (or minimal) twist of the 
%free 
eleven-dimensional supergravity multiplet recently computed by the second two authors, and we offer numerous consistency checks showing that the interactions  correctly  describe interacting twisted eleven-dimensional supergravity at the perturbative level. 
We prove that the global symmetry algebra of our model on flat space is an $L_\infty$ central extension of the infinite-dimensional simple exceptional super Lie algebra $E(5,10)$, following a recent suggestion of Cederwall in the context of the relevant pure spinor model. 
Twists of superconformal algebras map to the fields of our model on the complement of the support of a stack of M2 or M5 branes, laying the groundwork for a fully holomorphic version of twisted holography in this context.
\end{abstract}
\maketitle

>>>>

\title{Twisted eleven-dimensional supergravity}
\author{Surya Raghavendran}
\address{Perimeter Institute for Theoretical Physics \\ 31 Caroline Street North \\ 
Waterloo, Ontario N2L 2Y5\\ Canada}
\email{sraghavendran@perimeterinstitute.ca}
\author{Ingmar Saberi}
\address{Ludwig-Maximilians-Universit\"at M\"unchen \\ Fakult\"at f\"ur Physik \\ Theresienstra\ss{}e 37 \\ 80333 M\"unchen \\ Deutschland}
\email{i.saberi@physik.uni-muenchen.de}
\author{Brian R. Williams}
\address{School of Mathematics \\ University of Edinburgh \\ Edinburgh EH9 3FD \\ Scotland}
\email{brian.williams@ed.ac.uk}
\begin{abstract}
We construct a fully interacting holomorphic/topological theory in eleven dimensions that is defined on products of Calabi--Yau fivefolds with real one-manifolds. 
%The theory is a deformation of a BF theory based on divergence-free holomorphic vector fields on the fivefold. 
The theory describes a particular deformation of the cotangent bundle to the moduli space of complex structures on the fivefold.
Its field content matches the holomorphic (or minimal) twist of the 
%free 
eleven-dimensional supergravity multiplet recently computed by the second two authors, and we offer numerous consistency checks showing that the interactions correctly describe interacting twisted eleven-dimensional supergravity at the perturbative level. 
We prove that the global symmetry algebra of our model on flat space is an $L_\infty$ central extension of the infinite-dimensional simple exceptional super Lie algebra $E(5,10)$, following a recent suggestion of Cederwall in the context of the relevant pure spinor model. 
Twists of superconformal algebras map to the fields of our model on the complement of a stack of M2 or M5 branes, laying the groundwork for a fully holomorphic version of twisted holography in this context.
\end{abstract}
\maketitle
